Conference output

### 2018-05-30 Report/arne-conference.Rmd
Adds stats

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
```

@@

block_measure <- function(df, value){
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block43diff = sum(block4-block3, na.rm = T)/sum(block4+block3, na.rm = T),
              block41diff = sum(block4-block1, na.rm = T)/sum(block4+block1, na.rm = T))
}
```
Block 43 diff is as we discussed (block4 - block3)/(block4 + block3) and block41 is the forth and first.

@@

Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance")
ggplot(melt(df[,c(1,5)]), aes(x = condition, y = value)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean sum of errors improvement from block 3 to 4")

ggplot(melt(df[,c(1,6)]), aes(x = condition, y = value)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean sum of errors improvement from block 1 to 4")
```

@@

ggplot(melt(df[,c(1,5)]), aes(x = condition, y = value)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance improvement from block 3 to 4")

ggplot(melt(df[,c(1,6)]), aes(x = condition, y = value)) + geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance improvement from block 1 to 4")
```

>>>>

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(reshape2)
library(broom)

source('../Scripts/analysis-helpers.R')
sop_all <- read.table("../sop.csv", sep=";", header = T, stringsAsFactors = F)
walk_all <- read.table("../walk.csv", sep=";", header = T, stringsAsFactors = F)
conference_walk_all <- walk_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
conference_sop_all <- sop_all %>% filter(condition %in% c("vr-real", "real-real", "ve-real"))
```

@@

block_measure <- function(df, value){
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value)
  colnames(df_wide) <- c("condition","id", "block1","block2","block3","block4","block5","block6")
  df_wide %>% 
    group_by(condition) %>%
    summarise(block1.mean  = mean(block1, na.rm = T),
              block3.mean = mean(block3, na.rm = T),
              block4.mean = mean(block4, na.rm = T),
              block34.diff = sum(block3-block4, na.rm = T)/sum(block4+block3, na.rm = T),
              block34.se  = sqrt(var((block3-block4)/(block4+block3), na.rm = T)/sum(!is.na(block3-block4))),
              block14.diff = sum(block1-block4, na.rm = T)/sum(block4+block1, na.rm = T),
              block14.se = sqrt(var((block1-block4)/(block1+block4), na.rm = T)/sum(!is.na(block1-block4)))
  )
}
```
Block 43 diff is now flipped to (block4 - block3)/(block4 + block3) and block41 is the forth and first.

@@

Measure of overall sum of errors. Mean columns define mean sum of errors for all participants in that block
```{r, echo=F, warnings = F}
df <- block_measure(condition_all_sums, "sum.errors")
df
ggplot(melt(df[,1:4]), aes(x = condition, y = value, fill = variable)) + 
  geom_bar(stat = 'identity', position="dodge") + ylab("Mean normalised distance")

ggplot(df, aes(x = condition, y = block34.diff, fill = condition)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  geom_errorbar(aes(ymin=block34.diff-block34.se, ymax=block34.diff+block34.se), 
                width=.2, position=position_dodge(.9)) 
  ylab("Mean sum of errors improvement from block 3 to 4")

ggplot(df, aes(x = condition, y = block14.diff, fill = condition)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  geom_errorbar(aes(ymin=block14.diff-block14.se, ymax=block14.diff+block14.se), 
                width=.2, position=position_dodge(.9)) +
  ylab("Mean sum of errors improvement from block 1 to 4")
```

@@

ggplot(df, aes(x = condition, y = block34.diff, fill = condition)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  geom_errorbar(aes(ymin=block34.diff-block34.se, ymax=block34.diff+block34.se), 
                width=.2, position=position_dodge(.9)) +
  ylab("Mean normalised distance improvement from block 3 to 4")

ggplot(df, aes(x = condition, y = block14.diff, fill = condition)) + 
  geom_bar(stat = 'identity', position="dodge") + 
  geom_errorbar(aes(ymin=block14.diff-block14.se, ymax=block14.diff+block14.se), 
                width=.2, position=position_dodge(.9)) +
  ylab("Mean normalised distance improvement from block 1 to 4")
```

# Stats

## Block T tests

```{r, echo =F}
block_t_test <- function(df, block1, block2, value){
  df <- df %>% filter(exp_block_id %in% c(block1,block2))
  mean.na <- function(data){return(mean(data, na.rm = T))}
  df_wide <- dcast(df, condition + id ~ exp_block_id, value.var = value, fun.aggregate = mean.na)
  colnames(df_wide) <- c("condition","id", "block1","block2")
  df_wide %>% group_by(condition) %>% do(tidy(t.test(.$block1, .$block2, paired = T)))
}

### Block 3-4
Paired t tests between min normalised distance difference in blocks 3 and 4.
```{r}
block_t_test(conference_walk_all, 4, 3,"min_norm_distance")
```

And for number of errors
```{r}
block_t_test(conference_walk_all, 4, 3,"errors")
```

### Block 1 and 4
Paired t tests between min normalised distance difference in blocks 1 and 4.
```{r}
block_t_test(conference_walk_all, 4, 1,"min_norm_distance")
```
And for number of errors
```{r}
block_t_test(conference_walk_all, 4, 1,"errors")
```

### Block 1 and 6
Paired t tests between min normalised distance difference in blocks 1 and 6.
```{r}
block_t_test(conference_walk_all, 6, 1,"min_norm_distance")
```
And for number of errors
```{r}
block_t_test(conference_walk_all, 6, 1,"errors")
```

## Anova
This is simple mixed anova (for those three conditions) I know how to do in R. Not sure how to do contrasts and within add subject error variability, nor how to run post hocs. I expect Mike will be able to do that in his models for the paper.

```{r}
aov_block_distance <- aov(min_norm_distance~exp_block_id*condition, conference_walk_all)
summary(aov_block_distance)
```
